Microxanox - an R package for simulating an $MICR$obial ecosystem that can occupy $OX$ic or $ANOX$ic states.

### 2022-03-27 inst/manuscript/manuscript_microxanox.Rmd
Update manuscript_microxanox.Rmd

---
title: "Microxanox - an R package to simulate ..."
author:
- name: Rainer M Krug
  email: Rainer.Krug@uzh.ch & Rainer@krugs.de
  affiliation: University of Zürich
  footnote: Corresponding Author
- name: Owen L. Petchey
  email: Owen.Petchey@ieu.uzh.ch
  affiliation: University of Zürich
address:
- code: University of Zürich
  address: Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse
    190, 8057 Zurich
keywords: metadata quality; data curation; archival; long term storage; R package;
abstract: | 
  1. set the context for and purpose of the work;
  2. indicate the approach and methods;
  3. outline the main results;
  4. identify the conclusions and the wider implications.
bibliography: manuscript_bibliography.bib

@@

# Availability and Accessability of the Package
The package is available in a [github repo/](https://github.com/UZH-PEG/microxanox/). The newest version is also available under the [DOI](https://DOI) or via RUniverse [@REF_NEEDED]. This manuscript describes version 1.0 which is available under [DOI](https://DOI) or installable within R by using `remotes::install_github("UZH-PEG", ref = "v1.0")`.

@@

# The R Package

@@

## The modelling framework

@@

The individual simulation (`run_simulation()` function) is the working horse in this package. In this function, the ODEs are solved. The function needs only one parameter - an object as created by the function `new_runsim_parameter()`. One parameter of this object is the `strain_parameter` which can be created by the function `new_strain_parameter()`. For a detailed description of the parameter and how they are created please see the User Guide and which acomnpanies the package or is available at [User Guide](@LINK_NEEDED)

After the paramter object has been defined, it can be used in the `run_simulation()` function. The function returns an object which is identical to the parameter, except of an additional slot containing the results. This design produces a fully reproducible object as it can be used instead of a parameter object to be fed back into the `run_simulation()` function to run the simulation again from the parameter used to generate the results from.

@@

### Find a Steady State of the model

@@

## Extract Stability Measures
From the raw results returned by these `run_...()` functions, the stability measures can be extracted by using the function `get_stability_measures()`. These measures include non-linearity and hysteresis measures, of the response of the simulated system to environmental change.

>>>>

---
title: "Microxanox - an R package for simulating an $MICR$obial ecosystem that can occupy $OX$ic or $ANOX$ic states."
author:
- name: Rainer M Krug
  email: Rainer.Krug@uzh.ch & Rainer@krugs.de
  affiliation: University of Zürich
  footnote: Corresponding Author
- name: Owen L. Petchey
  email: Owen.Petchey@ieu.uzh.ch
  affiliation: University of Zürich
address:
- code: University of Zürich
  address: Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse
    190, 8057 Zurich
keywords: metadata quality; data curation; archival; long term storage; R package;
abstract: | 
  1. set the context for and purpose of the work;
  2. indicate the approach and methods;
  3. outline the main results;
  4. identify the conclusions and the wider implications.
bibliography: manuscript_bibliography.bib

@@

# Availability and Accessability of the package

The package is available in a [github repo/](https://github.com/UZH-PEG/microxanox/). The newest version is also available under the [DOI](https://DOI) or via RUniverse [@REF_NEEDED]. This manuscript describes version 1.0 which is available under [DOI](https://DOI) or installable within R by using `remotes::install_github("UZH-PEG", ref = "v1.0")`.

@@

# Package description

@@

## Reproducibility

@@

The individual simulation (`run_simulation()` function) is the working horse in this package. In this function, the ODEs are solved. The function needs only one argument - an object as created by the function `new_runsim_parameter()`. One parameter of this object is the `strain_parameter` which can be created by the function `new_strain_parameter()`. For a detailed description of the parameter and how they are created please see the User Guide and which acomnpanies the package or is available at [User Guide](@LINK_NEEDED)

After the parameter object has been defined, it can be used in the `run_simulation()` function. The function returns an object which is identical to the parameter, except of an additional slot containing the results. This design produces a fully reproducible object as it can be used instead of a parameter object to be fed back into the `run_simulation()` function to run the simulation again from the parameter used to generate the results from.

@@

### Finding a Steady State of the model

@@

## Extracting Stability Measures
From the raw results returned by these `run_...()` functions, the stability measures can be extracted by using the function `get_stability_measures()`. These measures include non-linearity and hysteresis measures, of the response of the simulated system to environmental change.
